Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
adds item_grade, e.g. "COR1002_8"

    item_PF = paste(`Course ID`, PF, sep = "_"),
    item_HL = paste(`Course ID`, HL, sep = "_")
    ) %>%
  rename(
    item = `Course ID`
  )
```

@@

    item_PF = paste(item, PF, sep = "_"),
    item_HL = paste(item, HL, sep = "_")
    )
```
### Transactions for Apriori
```{r making transactions}

@@

### CSPADE Algorithm
##TODO: FILTER FAILS AND LOW GRADE, paste item: e.g."COR1002_8"

>>>>

    item_PF = paste(`Course ID`, PF, sep = "_"),
    item_HL = paste(`Course ID`, HL, sep = "_"),
    item_Grade = paste(`Course ID`, Grade, sep = "_")
    ) %>%
  rename(
    item = `Course ID`
  )
```

@@

    item_PF = paste(item, PF, sep = "_"),
    item_HL = paste(item, HL, sep = "_"),
    item_Grade = paste(item, Grade_round, sep = "_")
    )
```
### Transactions for Apriori
```{r making transactions}

@@

### CSPADE Algorithm
##TODO:paste item: e.g."COR1002_8"
